---
title: "Simple document"
author: "Lindsey Abramson"
date: 2025-09-11
output: html_document
---

I'm an R Markdown document! 

```{r}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Section 3

This is where I'm going to talk about code chunks.

```{r eval = FALSE}
mean(samp)
sd(samp)
```

Let's make a plor and see how cool that is!
```{r}
plot_df = tibble(
  x=rnorm(1000, mean=1, sd=.5),
  y=1+2*x

)
```

# Learning assessment
This chunk does one of the LA

```{R}
la_df = 
  tibble(
    numeric_samp = rnorm(500, mean=1),
    abs_val_samp = abs(numeric_samp)
  )

ggplot(la_df, aes(x=abs_val_samp)) + geom_histogram()
```
To use inline code, I would do something like: "The sample size in the new dataframe is `r nrow(la_df)`"

Something mroe complex is "The mean of my new variable is `r 
mean (pull(la_df, abs_val_samp))`
`

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
